Vocabulary

### 2022-01-20 docs/00_participants.Rmd
Model comparisons with simpler models

```{r participants_summary_tab, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
participants %>% 
	left_join(distinct(attrition, participant, valid_participant)) %>% 
	filter(valid_participant) %>% 
	drop_na(valid_participant) %>% 
	count(location, age_group, lp) %>% 
	pivot_wider(names_from = "age_group", values_from = c("n"), values_fill = 0) %>% 
	gt(groupname_col = "location") %>% 
	cols_label(
		lp = md("**Language profile**"),
		`21 months` = md("**21 months**"),
		`25 months` = md("**25 months**"),
		`30 months` = md("**30 months**")
	) %>% 
	as_raw_html()
```

>>>>

```{r participants_summary_tab, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
participants_tab <- participants %>% 
	left_join(distinct(attrition, participant, valid_participant)) %>% 
	filter(valid_participant) %>% 
	drop_na(valid_participant) %>% 
	count(location, age_group, lp) %>% 
	pivot_wider(names_from = "age_group", values_from = c("n"), values_fill = 0) %>% 
	gt(groupname_col = "location") %>% 
	cols_label(
		lp = md("**Language profile**"),
		`21 months` = md("**21 months**"),
		`25 months` = md("**25 months**"),
		`30 months` = md("**30 months**")
	)

gtsave(participants_tab, here("img", "participants_tab.png"))
as_raw_html(participants_tab)
```

### 2022-01-20 docs/02_vocabulary.Rmd
Model comparisons with simpler models

```{r vocabulary_l1, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4}
sample_size <- participants %>% 
	filter(valid_participant, !is.na(vocab_size_l1)) %>% 
	count(age_group, location)

sample_size_lp <- participants %>% 
	filter(valid_participant, !is.na(vocab_size_l1)) %>% 
	count(age_group, lp, location) %>% 
	mutate(
		age_group = case_when(
			age_group=="21 months" ~ paste0(age_group, " (N = ", sample_size$n[1], ")"),
			age_group=="25 months" ~ paste0(age_group, " (N = ", sample_size$n[2], ")"),
			age_group=="30 months" ~ paste0(age_group, " (N = ", sample_size$n[3], ")")
		)
	)

# vocabulary
participants %>% 
	mutate(
		age_group = case_when(
			age_group=="21 months" ~ paste0(age_group, " (N = ", sample_size$n[1], ")"),
			age_group=="25 months" ~ paste0(age_group, " (N = ", sample_size$n[2], ")"),
			age_group=="30 months" ~ paste0(age_group, " (N = ", sample_size$n[3], ")")
		)
	) %>% 
	drop_na(lp) %>%
	filter(valid_participant) %>% 
	ggplot() +
	facet_wrap(~age_group, scales = "free_x") +
	geom_hline(yintercept = 0.5, colour = "black", linetype = "dotted") +
	stat_pointinterval(
		aes(lp, vocab_size_l1, group = lp),
		position = position_nudge(x = 0.2),
		.width = c(0.95, 0.89, 0.50),
		point_size = 3
	) +
	geom_point(
		aes(lp, vocab_size_l1, color = lp),
		shape = 1, size = 3, stroke = 1.5, alpha = 0.75,
		position = position_jitter(width = 0.1, seed = 888)
	) +
	geom_text(
		data = sample_size_lp,
		aes(x = 1.5, y = 0, label = paste0("N = ", n), group = lp),
		show.legend = FALSE, position = position_dodge(width = 2)
	) +
	labs(
		y = "Receptive vocabulary (L1)", colour = "Group", fill = "Group",
		title = "Total vocabulary size",
		subtitle = "Percentage of words in L1+L2 reported to be understood from the vocabulary checklist"
	) +
	guides(colour = "none") +
	scale_color_manual(aesthetics = "slab_color", values = pal_futurama()(2)) +
	scale_y_continuous(limits = c(0, 1), labels = percent) +
	theme(
		legend.title = element_blank(),
		legend.position = "top",
		panel.grid.major.x = element_blank(),
		axis.title.x = element_blank(),
		axis.text = element_text(size = 9)
	)

@@

```{r vocabulary_total, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4}
sample_size <- participants %>% 
	filter(valid_participant, !is.na(vocab_size_total)) %>% 
	count(age_group, location)

# vocabulary
participants %>% 
	mutate(
		age_group = case_when(
			age_group=="21 months" ~ paste0(age_group, " (N = ", sample_size$n[1], ")"),
			age_group=="25 months" ~ paste0(age_group, " (N = ", sample_size$n[2], ")"),
			age_group=="30 months" ~ paste0(age_group, " (N = ", sample_size$n[3], ")")
		)
	) %>% 
	drop_na(lp) %>%
	filter(valid_participant) %>% 
	ggplot() +
	facet_wrap(~age_group, scales = "free_x") +
	geom_hline(yintercept = 0.5, colour = "black", linetype = "dotted") +
	stat_pointinterval(
		aes(lp, vocab_size_total, group = lp),
		position = position_nudge(x = 0.2),
		.width = c(0.95, 0.89, 0.50),
		point_size = 3
	) +
	geom_point(
		aes(lp, vocab_size_total, color = lp),
		shape = 1, size = 3, stroke = 1.5, alpha = 0.75,
		position = position_jitter(width = 0.1, seed = 888)
	) +
	geom_text(
		data = sample_size_lp,
		aes(x = 1.5, y = 0, label = paste0("N = ", n), group = lp),
		show.legend = FALSE, position = position_dodge(width = 2)
	) +
	labs(
		y = "Receptive vocabulary (L1)", colour = "Group", fill = "Group",
		title = "L1 vocabulary size",
		subtitle = "Percentage of words in L1 reported to be understood from the vocabulary checklist"
	) +
	guides(colour = "none") +
	scale_color_manual(aesthetics = "slab_color", values = pal_futurama()(2)) +
	scale_y_continuous(limits = c(0, 1), labels = percent) +
	theme(
		legend.title = element_blank(),
		legend.position = "top",
		panel.grid.major.x = element_blank(),
		axis.title.x = element_blank(),
		axis.text = element_text(size = 9)
	)

@@

draws <- gather_draws(fit_total, `b_.*`, `sigma`, regex = TRUE) %>% 
	mutate(
		.value = ifelse(.variable=="sigma", inv_logit(.value), .value),
		.variable_name = str_replace_all(.variable, str_repl),
		type = case_when(
			str_detect(.variable, "E2") ~ "Quadratic time",
			str_detect(.variable, "E3") ~ "Cubic time",
			str_detect(.variable, "time_bin") ~ "Linear time",
			str_detect(.variable, "sigma") ~ "Error",
			TRUE ~ "Main effects"
		) %>% 
			factor(levels = c("Main effects", "Linear time", "Quadratic time", "Cubic time", "Error"), ordered = TRUE)
	)

>>>>

```{r vocabulary_l1, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4}
sample_size <- participants %>% 
	filter(
		participant %in% fit_l1_4$data$participant
	) %>% 
	count(age_group, location)

sample_size_lp <- participants %>% 
	filter(
		participant %in% fit_l1_4$data$participant
	) %>% 
	count(age_group, lp, location) %>% 
	mutate(
		age_group = case_when(
			age_group=="21 months" ~ paste0(age_group, " (N = ", sample_size$n[1], ")"),
			age_group=="25 months" ~ paste0(age_group, " (N = ", sample_size$n[2], ")"),
			age_group=="30 months" ~ paste0(age_group, " (N = ", sample_size$n[3], ")")
		)
	)

# vocabulary
participants %>% 
	mutate(
		age_group = case_when(
			age_group=="21 months" ~ paste0(age_group, " (N = ", sample_size$n[1], ")"),
			age_group=="25 months" ~ paste0(age_group, " (N = ", sample_size$n[2], ")"),
			age_group=="30 months" ~ paste0(age_group, " (N = ", sample_size$n[3], ")")
		)
	) %>% 
	drop_na(lp) %>%
	filter(valid_participant) %>% 
	ggplot() +
	facet_wrap(~age_group, scales = "free_x") +
	geom_hline(yintercept = 0.5, colour = "black", linetype = "dotted") +
	stat_pointinterval(
		aes(lp, vocab_size_l1, group = lp),
		position = position_nudge(x = 0.2),
		.width = c(0.95, 0.89, 0.50),
		point_size = 3
	) +
	geom_point(
		aes(lp, vocab_size_l1, color = lp),
		shape = 1, size = 3, stroke = 1.5, alpha = 0.75,
		position = position_jitter(width = 0.1, seed = 888)
	) +
	geom_text(
		data = sample_size_lp,
		aes(x = 1.5, y = 0, label = paste0("N = ", n), group = lp),
		show.legend = FALSE, position = position_dodge(width = 2)
	) +
	labs(
		y = "Receptive vocabulary (L1)", colour = "Group", fill = "Group",
		title = "L1 vocabulary size",
		subtitle = "Percentage of words in L1 reported to be understood from the vocabulary checklist"
	) +
	guides(colour = "none") +
	scale_color_manual(aesthetics = "slab_color", values = pal_futurama()(2)) +
	scale_y_continuous(limits = c(0, 1), labels = percent) +
	theme(
		legend.title = element_blank(),
		legend.position = "top",
		panel.grid.major.x = element_blank(),
		axis.title.x = element_blank(),
		axis.text = element_text(size = 9)
	)

ggsave(here("img", "vocab_l1.png"))

@@

```{r vocabulary_total, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4}
sample_size <- participants %>% 
	filter(participant %in% fit_total_4$data$participant) %>% 
	count(age_group, location)

sample_size_lp <- participants %>% 
	filter(participant %in% fit_total_4$data$participant) %>% 
	count(age_group, lp, location) %>% 
	mutate(
		age_group = case_when(
			age_group=="21 months" ~ paste0(age_group, " (N = ", sample_size$n[1], ")"),
			age_group=="25 months" ~ paste0(age_group, " (N = ", sample_size$n[2], ")"),
			age_group=="30 months" ~ paste0(age_group, " (N = ", sample_size$n[3], ")")
		)
	)

# vocabulary
participants %>% 
	mutate(
		age_group = case_when(
			age_group=="21 months" ~ paste0(age_group, " (N = ", sample_size$n[1], ")"),
			age_group=="25 months" ~ paste0(age_group, " (N = ", sample_size$n[2], ")"),
			age_group=="30 months" ~ paste0(age_group, " (N = ", sample_size$n[3], ")")
		)
	) %>% 
	drop_na(lp) %>%
	filter(valid_participant) %>% 
	ggplot() +
	facet_wrap(~age_group, scales = "free_x") +
	geom_hline(yintercept = 0.5, colour = "black", linetype = "dotted") +
	stat_pointinterval(
		aes(lp, vocab_size_total, group = lp),
		position = position_nudge(x = 0.2),
		.width = c(0.95, 0.89, 0.50),
		point_size = 3
	) +
	geom_point(
		aes(lp, vocab_size_total, color = lp),
		shape = 1, size = 3, stroke = 1.5, alpha = 0.75,
		position = position_jitter(width = 0.1, seed = 888)
	) +
	geom_text(
		data = sample_size_lp,
		aes(x = 1.5, y = 0, label = paste0("N = ", n), group = lp),
		show.legend = FALSE, position = position_dodge(width = 2)
	) +
	labs(
		y = "Receptive vocabulary (total)", colour = "Group", fill = "Group",
		title = "Total vocabulary size",
		subtitle = "Percentage of words in L1+L2 reported to be understood from the vocabulary checklist"
	) +
	guides(colour = "none") +
	scale_color_manual(aesthetics = "slab_color", values = pal_futurama()(2)) +
	scale_y_continuous(limits = c(0, 1), labels = percent) +
	theme(
		legend.title = element_blank(),
		legend.position = "top",
		panel.grid.major.x = element_blank(),
		axis.title.x = element_blank(),
		axis.text = element_text(size = 9)
	)

ggsave(here("img", "vocab_total.png"))
```

@@

draws <- gather_draws(fit_total_4, `b_.*`, `sigma`, regex = TRUE) %>% 
	mutate(
		.value = ifelse(.variable=="sigma", inv_logit(.value), .value),
		.variable_name = str_replace_all(.variable, str_repl),
		type = case_when(
			str_detect(.variable, "E2") ~ "Quadratic time",
			str_detect(.variable, "E3") ~ "Cubic time",
			str_detect(.variable, "time_bin") ~ "Linear time",
			str_detect(.variable, "sigma") ~ "Error",
			TRUE ~ "Main effects"
		) %>% 
			factor(levels = c("Main effects", "Linear time", "Quadratic time", "Cubic time", "Error"), ordered = TRUE)
	)
